\documentclass{article}

\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{amsthm}

\setlength{\textwidth}{15cm}
\setlength{\textheight}{21cm}
\setlength{\topmargin}{0cm}
\setlength{\headsep}{0.5cm}
\setlength{\headheight}{0.5cm}
\setlength{\oddsidemargin}{0.25pt}
\setlength{\evensidemargin}{0.25pt}
\setlength{\parindent}{0pt}
\setlength{\parskip}{5pt}

\makeatletter
\newfont{\footsc}{cmcsc10 at 8truept}
\newfont{\footbf}{cmbx10 at 8truept}
\newfont{\footrm}{cmr10 at 10truept}

\renewcommand{\footrulewidth}{0.4pt}

\pagestyle{fancy}
\fancyhead[LO, LE]{{\sc COSC} 341: Assignment 2}

\begin{document}


\noindent {\bf Due Date: Friday 29 April, 4pm}

Please submit a {\bf PDF} by email to: \href{mailto:teaching@biods.org}{teaching@biods.org} with subject ``341 Assignment 2''.
Make sure that your name and ID number are on the PDF called: YourName\_assignment2.pdf

What you hand in should be all your own work.

Note that \textbf{marks might be deduced} if you fail to follow the above instructions.
Do let us know if you find them challenging.

\section*{Questions}

\begin{enumerate}
\item Let $\Sigma = \{0, 1\}$, and for a word $w \in \Sigma^*$ define $\bar{w}$ to be the word obtained by exchanging $0$'s and $1$'s in $w$ (so if $w = 101$ then $\bar{w} = 010$).
Consider the language $L$ over the alphabet $\{0, 1, 2\}$ consisting of all words of the form $w 2 \bar{w}$, where $w \in
\Sigma^*$.
\begin{enumerate}
\item Is $L$ regular? Prove it. (\textbf{2 marks})
\item Is $L$ context-free? Prove it. (\textbf{2 mark})
\end{enumerate}

\item Design a Turing machine to compute $f(x) = 2^x$.
Use comments (or self-explanatory state names, or both) in your code to make it readable.
Both correctness and readability of your code will be marked. (\textbf{3 marks})

\item Show that, if there is a language $Q$ that is both in $\mathcal P$ and $\mathcal NP$-complete, then $\mathcal P = \mathcal{NP}$. (\textbf{3 marks})
\end{enumerate}
\end{document}
